Points Above Replacement: A New NBA Metric to Evaluate Player Performance

### 2022-04-04 Manuscript/Manuscript.tex
Add files via upload

\usepackage{xr-hyper}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{listings}
\usepackage{rotating, graphicx}
\usepackage{booktabs, natbib}

@@

\usepackage{xr}
%\externaldocument{isgee}
%\externaldocument{supp}

@@

\newenvironment{comment}%
{\begin{quoting}\noindent\small\it\ignorespaces%
  }{\end{quoting}}
 \title{Points Above Replacement: A New NBA Metric to Evaluate Player Performance}
\author{
Brian Krikorian*, Jun Yan \\ \medskip 
Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
Students: brian.krikorian@uconn.edu* \\
Mentor: jun.yan@uconn.edu 
}
\begin{document}

% Abstracts are required.
\section*{Abstract}
In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other 
reason not playing have a significant impact on said prediction. Baseball uses a statistic called Wins Above 
Replacement, or WAR, to tell how many wins a team would gain or lose if they replaced a certain player 
with one who is league average. The goal of this paper is to create a similar statistic, called Points Above 
Replacement, or PAR, that uses statistics from throughout the season to predict how many points a team 
gains or loses by missing a certain player, and thus having to replace him with one who is "league 
average". The statistic is standardized and adjusted by both position and value to a player's given team. 
The model roughly follows the calculation of WAR in baseball, assigning values to points created on offense 
and defense, as well as a positional and team adjustment. A comparison with the created metric along with 
other well-known advanced player metrics is done via a multiple regression.

@@

\section{Methods}
% Should dive more in depth about how everything was obtained, calculated, etc.
The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but 
also took influences from other advanced basketball statistics. WAR is based on Offensive and Defensive 
Runs, which are calculated subjectively via attributes of the game such as hitting, base running, fielding, 
and so forth. The subjectivity is in the coefficients chosen to scale statistics which impact Offensive and 
Defensive Runs. Thus, there are actually an infinite different kinds of WAR in baseball, depending on which 
method of calculating Offensive and Defensive Runs is used. Similarly, PAR is created by calculating 
Offensive and Defensive Points statistics, to analyze how many points a player adds for his team, and how 
many he prevents the other team from scoring. Using the basic offensive statistics of Effective Field Goal 
Percentage, Three Point Percentage, Free Throw Percentage, Offensive Rebounds, Assists, Points, and 
Turnovers, we assign a coefficient to them based on how important they are for a given position. Point 
guards are expected to pass more than centers, and a point guard's passing ability has more value to his 
team than a center, so more weight is placed on that statistic for point guards. This goes for all positions, 
and a coefficient matrix of a constant scale is created. That is to say, assists have a coefficient from point 
guards, shooting guards, small forwards, power forwards, and centers, respectively, of 4, 3.5, 3, 2.5, and 2. 
The coefficient by position method is one similar to that of Box Plus Minus, another advanced NBA metric. 
The position a player was assigned for the calculation was the position where he played the most minutes 
throughout the 2020-2021 season. This coefficient method gives a clean scaling into the calculation of 
Offensive Points. Some statistics, such as Points and Effective Field Goal Percentage, are equally 
important, regardless of the position of a given player. Thus, these statistics have a constant coefficient that 
does not change. Once all coefficients were applied to all statistics, the sum was taken to give Offensive 
Points. The exact same method was applied to the Defensive Points calculation, but used the basic 
defensive statistics of Defensive Rebounds, Total Rebounds, Steals, Blocks, and Personal Fouls. As 
turnovers and personal fouls are not desirable amongst players, the coefficients for these statistics is 
negative, which allows for a scale of not only the good a player does, but also what they do poorly. This 
coefficient method is similar to the Positional Adjustment metric applied in WAR calculation, which seeks to 
adjust a player's importance based on what is expected of their position.

@@

\begin{table}[tbp]
  \caption{PAR Values from the Entire NBA}
  \label{tab:NBAtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Position & Team & PAR\\
  \midrule
 1 & Nikola Jokic & C & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & C & Orlando Magic & 6.55\\
  \midrule
 3 & Julius Randle & PF & New York Knicks & 6.49\\
  \midrule
 4 & Luka Doncic & PG & Dallas Mavericks & 4.61\\
  \midrule
 5 & Damian Lillard & PG & Portland Trail Blazers & 4.47\\
  \midrule
 6 & Giannis Antetokounmpo & PF & Milwaukee Bucks & 4.21\\
  \midrule
 7 & Stephen Curry & PG & Golden State Warriors & 4.17\\
  \midrule
 8 & Russell Westbrook & PG & Washington Wizards & 4.05\\
  \midrule
 9 & Jayson Tatum & SF & Boston Celtics & 3.96\\
  \midrule
 10 & Domanatas Sabonis & PF & Indiana Pacers & 3.21\\
  \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[tbp]
  \caption{PAR Values from all Point Guards}
  \label{tab:PGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Luka Doncic & Dallas Mavericks & 4.61\\
  \midrule
 2 & Damian Lillard & Portland Trail Blazers & 4.47\\
  \midrule
 3 & Stephen Curry & Golden State Warriors & 4.17\\
  \midrule
 4 & Russell Westbrook & Washington Wizards & 4.05\\
  \midrule
 5 & Trae Young & Atlanta Hawks & 2.69\\
  \midrule
 6 & De'Aaron Fox & Sacramento Kings & 1.94\\
  \midrule
 7 & Chris Paul & Phoenix Suns & 1.93\\
  \midrule
 8 & Kyrie Irving & Brooklyn Nets & 1.74\\
  \midrule
 9 & Dejounte Murray & San Antonio Spurs & 1.64\\
  \midrule
 10 & Ja Morant & Memphis Grizzlies & 1.45\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Shooting Guards}
  \label{tab:SGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Bradley Beal & Washington Wizards & 3.17\\
  \midrule
 2 & Devin Booker & Phoenix Suns & 2.74\\
  \midrule
 3 & Terry Rozier & Charlotte Hornets & 2.59\\
  \midrule
 4 & Zach Lavine & Chicago Bulls & 2.29\\
  \midrule
 5 & RJ Barrett & New York Knicks & 2.28\\
  \midrule
 6 & Anthony Edwards & Minnesota Timberwolves & 2.22\\
  \midrule
 7 & Jaylen Brown & Boston Celtics & 1.87\\
  \midrule
 8 & Collin Sexton & Cleveland Cavaliers & 1.85\\
  \midrule
 9 & Buddy Hield & Sacramento Kings & 1.72\\
  \midrule
 10 & Norman Powell & Toronto Raptors & 1.37\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Small Forwards}
  \label{tab:SFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Jayson Tatum & Boston Celtics & 3.96\\
  \midrule
 2 & Khris Middleton & Milwaukee Bucks & 2.39\\
  \midrule
 3 & Brandon Ingram & New Orleans Pelicans & 2.13\\
  \midrule
 4 & Kawhi Leonard & Los Angeles Clippers & 1.58\\
  \midrule
 5 & Paul George & Los Angeles Clippers & 1.44\\
  \midrule
 6 & Michael Porter Jr. & Denver Nuggets & 1.42\\
  \midrule
 7 & Jimmy Butler & Miami Heat & 1.41\\
  \midrule
 8 & Bojan Bogdonavic & Utah Jazz & 1.35\\
  \midrule
 9 & Mikal Bridges & Phoenix Suns & 1.19\\
  \midrule
 10 & Jerami Grant & Detroit Pistons & 1.14\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Power Forwards}
  \label{tab:PFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Julius Randle & New York Knicks & 6.49\\
  \midrule
 2 & Giannis Antetokounmpo & Milwaukee Bucks & 4.21\\
  \midrule
 3 & Domanatas Sabonis & Indiana Pacers & 3.21\\
  \midrule
 4 & Zion Williamson & New Orleans Pelicans & 3.07\\
  \midrule
 5 & Andrew Wiggins & Golden State Warriors & 2.26\\
  \midrule
 6 & Demar Derozan & San Antonio Spurs & 1.88\\
  \midrule
 7 & Tobias Harris & Philadelphia 76ers & 1.87\\
  \midrule
 8 & Pascal Siakam & Toronto Raptors & 1.72\\
  \midrule
 9 & John Collins & Atlanta Hawks & 1.35\\
  \midrule
 10 & Harrison Barnes & Sacramento Kings & 1.11\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[tbp]
  \caption{PAR Values from all Centers}
  \label{tab:Ctable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Nikola Jokic & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & Orlando Magic & 6.55\\
  \midrule
 3 & Rudy Gobert & Utah Jazz & 3.10\\
  \midrule
 4 & Bam Adebayo & Miami Heat & 2.78\\
  \midrule
 5 & Joel Embiid & Philadelphia 76ers & 2.26\\
  \midrule
 6 & Clint Capela & Atlanta Hawks & 2.25\\
  \midrule
 7 & DeAndre Ayton & Phoenix Suns & 2.11\\
  \midrule
 8 & Jonas Valanciunas & Memphis Grizzlies & 1.98\\
  \midrule
 9 & Karl-Anthony Towns & Minnesota Timberwolves & 1.82\\
  \midrule
 10 & Kelly Olynyk & Miami Heat & 1.39\\
  \bottomrule
\end{tabular}
\end{table}

PAR will also be compared with the 4 accepted advanced metrics that were used as regressors in the 
multiple regression on PAR. These include Player Efficiency Rating, Win Shares, Box Plus Minus, and 
Value Over Replacement Player
%PAR vs. PER
%PAR vs. WS
%PAR vs. BPM
%PAR vs. VORP

@@

>>>>

\usepackage{float}
\usepackage{xr-hyper}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{listings}
\usepackage{rotating, graphicx}
\usepackage{booktabs, natbib}

@@

\usepackage{xr}

@@

\newenvironment{comment}%
{\begin{quoting}\noindent\small\it\ignorespaces%
  }{\end{quoting}}
 \title{Points Above Replacement: A New NBA Metric to Evaluate Player Performance}
\author{
Brian Krikorian*, Jun Yan \\ \medskip 
Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
Students: brian.krikorian@uconn.edu* \\
Mentor: jun.yan@uconn.edu 
}

\begin{document}

\begin{titlepage}
   \begin{center}
       \vspace*{1cm}
       \Huge
       \textbf{Points Above Replacement}

       \Large
       \vspace{0.5cm}
        A New NBA Metric to Evaluate Player Performance

       \vspace{1.5cm}

       \textbf{Brian Krikorian}

       \vfill

       \includegraphics[width=0.4\textwidth]{UCONNwordmark}

       \vfill

       Mentor: Jun Yan\\
       Data Science

       \vspace{0.8cm}

       \includegraphics[width=0.4\textwidth]{UCONNoakleaf}

        \Large    
       Department of Statistics\\
       University of Connecticut\\
       Storrs, CT\\

   \end{center}
\end{titlepage}
% Abstracts are required.
\section*{Abstract}
In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other 
reason not playing have a significant impact on said prediction. Baseball uses a statistic called Wins Above 
Replacement, or WAR, to tell how many wins a team would gain or lose if they replaced a certain player 
with one who is league average. The goal of this paper is to create a similar statistic, called Points Above 
Replacement, or PAR, that uses statistics from throughout the season to predict how many points a team 
gains or loses by missing a certain player, and thus having to replace him with one who is "league 
average". The statistic is standardized and adjusted by both position and value to a player's given team. 
The model roughly follows the calculation of WAR in baseball, assigning values to points created on offense 
and defense, as well as a positional and team adjustment. A comparison with the created metric along with 
other well-known advanced player metrics is done via a multiple regression.

@@

\section{Methods}
% Should dive more in depth about how everything was obtained, calculated, etc.

The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but 
also took influences from other advanced basketball statistics. WAR is based on Offensive and Defensive 
Runs, which are calculated subjectively via attributes of the game such as hitting, base running, fielding, 
and so forth. The subjectivity is in the coefficients chosen to scale statistics which impact Offensive and 
Defensive Runs. Thus, there are actually an infinite different kinds of WAR in baseball, depending on which 
method of calculating Offensive and Defensive Runs is used. Similarly, PAR is created by calculating 
Offensive and Defensive Points statistics, to analyze how many points a player adds for his team, and how 
many he prevents the other team from scoring. Using the basic offensive statistics of Effective Field Goal 
Percentage, Three Point Percentage, Free Throw Percentage, Offensive Rebounds, Assists, Points, and 
Turnovers, we assign a coefficient to them based on how important they are for a given position. Point 
guards are expected to pass more than centers, and a point guard's passing ability has more value to his 
team than a center, so more weight is placed on that statistic for point guards. This goes for all positions, 
and a coefficient matrix of a constant scale is created. That is to say, assists have a coefficient from point 
guards, shooting guards, small forwards, power forwards, and centers, respectively, of 4, 3.5, 3, 2.5, and 2. 
The coefficient by position method is one similar to that of Box Plus Minus, another advanced NBA metric. 
The position a player was assigned for the calculation was the position where he played the most minutes 
throughout the 2020-2021 season. This coefficient method gives a clean scaling into the calculation of 
Offensive Points. Some statistics, such as Points and Effective Field Goal Percentage, are equally 
important, regardless of the position of a given player. Thus, these statistics have a constant coefficient that 
does not change. Once all coefficients were applied to all statistics, the sum was taken to give Offensive 
Points. The exact same method was applied to the Defensive Points calculation, but used the basic 
defensive statistics of Defensive Rebounds, Total Rebounds, Steals, Blocks, and Personal Fouls. As 
turnovers and personal fouls are not desirable amongst players, the coefficients for these statistics is 
negative, which allows for a scale of not only the good a player does, but also what they do poorly. This 
coefficient method is similar to the Positional Adjustment metric applied in WAR calculation, which seeks to 
adjust a player's importance based on what is expected of their position. The coefficients for each position are listed below.

\vfill
\begin{table}[H]
  \caption{Coefficients for Each Statistic in Offensive and Defensive Points}
  \label{tab:Coefficientstable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Statistic & Point Guard & Shooting Guard & Small Forward & Power Forward & Center\\
  \midrule
 Effective FG Percentage & 200 & 200 & 200 & 200 & 200\\
 \midrule
 3 Point Percentage & 300 & 275 & 250 & 225 & 200\\
 \midrule
 Free Throw Percentage & 100 & 90 & 80 & 70 & 60\\
 \midrule
 Offensive Rebounds & 1 & 1.5 & 2 & 2.5 & 3\\
 \midrule
 Assists & 4 & 3.5 & 3 & 2.5 & 2\\
 \midrule
 Points & 2 & 2 & 2 & 2 & 2\\
 \midrule
 Turnovers & -5 & -4.5 & -4 & -3.5 & -3\\
 \midrule
 Defensive Rebounds & 2 & 2.5 & 3 & 3.5 & 4\\
 \midrule
 Total Rebounds & 3 & 3.25 & 3.5 & 3.75 & 4\\
 \midrule
 Steals & 5 & 4.5 & 4 & 3.5 & 3\\
 \midrule
 Blocks & 3 & 3.5 & 4 & 4.5 & 5\\
 \midrule
 Personal Fouls & -3 & -3 & -3 & -3 & -3\\
  \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
  \caption{PAR Values from the Entire NBA}
  \label{tab:NBAtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Position & Team & PAR\\
  \midrule
 1 & Nikola Jokic & C & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & C & Orlando Magic & 6.55\\
  \midrule
 3 & Julius Randle & PF & New York Knicks & 6.49\\
  \midrule
 4 & Luka Doncic & PG & Dallas Mavericks & 4.61\\
  \midrule
 5 & Damian Lillard & PG & Portland Trail Blazers & 4.47\\
  \midrule
 6 & Giannis Antetokounmpo & PF & Milwaukee Bucks & 4.21\\
  \midrule
 7 & Stephen Curry & PG & Golden State Warriors & 4.17\\
  \midrule
 8 & Russell Westbrook & PG & Washington Wizards & 4.05\\
  \midrule
 9 & Jayson Tatum & SF & Boston Celtics & 3.96\\
  \midrule
 10 & Domanatas Sabonis & PF & Indiana Pacers & 3.21\\
  \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
  \caption{PAR Values from all Point Guards}
  \label{tab:PGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Luka Doncic & Dallas Mavericks & 4.61\\
  \midrule
 2 & Damian Lillard & Portland Trail Blazers & 4.47\\
  \midrule
 3 & Stephen Curry & Golden State Warriors & 4.17\\
  \midrule
 4 & Russell Westbrook & Washington Wizards & 4.05\\
  \midrule
 5 & Trae Young & Atlanta Hawks & 2.69\\
  \midrule
 6 & De'Aaron Fox & Sacramento Kings & 1.94\\
  \midrule
 7 & Chris Paul & Phoenix Suns & 1.93\\
  \midrule
 8 & Kyrie Irving & Brooklyn Nets & 1.74\\
  \midrule
 9 & Dejounte Murray & San Antonio Spurs & 1.64\\
  \midrule
 10 & Ja Morant & Memphis Grizzlies & 1.45\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
  \caption{PAR Values from all Shooting Guards}
  \label{tab:SGtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Bradley Beal & Washington Wizards & 3.17\\
  \midrule
 2 & Devin Booker & Phoenix Suns & 2.74\\
  \midrule
 3 & Terry Rozier & Charlotte Hornets & 2.59\\
  \midrule
 4 & Zach Lavine & Chicago Bulls & 2.29\\
  \midrule
 5 & RJ Barrett & New York Knicks & 2.28\\
  \midrule
 6 & Anthony Edwards & Minnesota Timberwolves & 2.22\\
  \midrule
 7 & Jaylen Brown & Boston Celtics & 1.87\\
  \midrule
 8 & Collin Sexton & Cleveland Cavaliers & 1.85\\
  \midrule
 9 & Buddy Hield & Sacramento Kings & 1.72\\
  \midrule
 10 & Norman Powell & Toronto Raptors & 1.37\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
  \caption{PAR Values from all Small Forwards}
  \label{tab:SFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Jayson Tatum & Boston Celtics & 3.96\\
  \midrule
 2 & Khris Middleton & Milwaukee Bucks & 2.39\\
  \midrule
 3 & Brandon Ingram & New Orleans Pelicans & 2.13\\
  \midrule
 4 & Kawhi Leonard & Los Angeles Clippers & 1.58\\
  \midrule
 5 & Paul George & Los Angeles Clippers & 1.44\\
  \midrule
 6 & Michael Porter Jr. & Denver Nuggets & 1.42\\
  \midrule
 7 & Jimmy Butler & Miami Heat & 1.41\\
  \midrule
 8 & Bojan Bogdonavic & Utah Jazz & 1.35\\
  \midrule
 9 & Mikal Bridges & Phoenix Suns & 1.19\\
  \midrule
 10 & Jerami Grant & Detroit Pistons & 1.14\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
  \caption{PAR Values from all Power Forwards}
  \label{tab:PFtable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Julius Randle & New York Knicks & 6.49\\
  \midrule
 2 & Giannis Antetokounmpo & Milwaukee Bucks & 4.21\\
  \midrule
 3 & Domanatas Sabonis & Indiana Pacers & 3.21\\
  \midrule
 4 & Zion Williamson & New Orleans Pelicans & 3.07\\
  \midrule
 5 & Andrew Wiggins & Golden State Warriors & 2.26\\
  \midrule
 6 & Demar Derozan & San Antonio Spurs & 1.88\\
  \midrule
 7 & Tobias Harris & Philadelphia 76ers & 1.87\\
  \midrule
 8 & Pascal Siakam & Toronto Raptors & 1.72\\
  \midrule
 9 & John Collins & Atlanta Hawks & 1.35\\
  \midrule
 10 & Harrison Barnes & Sacramento Kings & 1.11\\
  \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
  \caption{PAR Values from all Centers}
  \label{tab:Ctable}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Rank & Player & Team & PAR\\
  \midrule
 1 & Nikola Jokic & Denver Nuggets & 7.69\\
  \midrule
 2 & Nikola Vucevic & Orlando Magic & 6.55\\
  \midrule
 3 & Rudy Gobert & Utah Jazz & 3.10\\
  \midrule
 4 & Bam Adebayo & Miami Heat & 2.78\\
  \midrule
 5 & Joel Embiid & Philadelphia 76ers & 2.26\\
  \midrule
 6 & Clint Capela & Atlanta Hawks & 2.25\\
  \midrule
 7 & DeAndre Ayton & Phoenix Suns & 2.11\\
  \midrule
 8 & Jonas Valanciunas & Memphis Grizzlies & 1.98\\
  \midrule
 9 & Karl-Anthony Towns & Minnesota Timberwolves & 1.82\\
  \midrule
 10 & Kelly Olynyk & Miami Heat & 1.39\\
  \bottomrule
\end{tabular}
\end{table}

PAR will also be compared with the 4 accepted advanced metrics that were used as regressors in the 
multiple regression on PAR. These include Player Efficiency Rating, Win Shares, Box Plus Minus, and 
Value Over Replacement Player

\begin{figure}[H]
  \centering
  \includegraphics[scale = 0.6]{PERvsPAR}
  \caption{Player Efficiency Ratings (x) vs. Points Above Replacement (y)}
  \label{fig:Fig1}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale = 0.6]{WSvsPAR}
  \caption{Win Shares (x) vs. Points Above Replacement (y)}
  \label{fig:Fig2}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale = 0.6]{BPMvsPAR}
  \caption{Box Plus Minus (x) vs. Points Above Replacement (y)}
  \label{fig:Fig3}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale = 0.6]{VORPvsPAR}
  \caption{Value Over Replacement Player (x) vs. Points Above Replacement (y)}
  \label{fig:Fig4}
\end{figure}

It can be seen that the graphs of PAR and Win Shares, as well as PAR and Value Over Replacement Player 
fit nicely, with a relatively positive and linear correlation. However, the graphs of PAR and Box Plus Minus, 
as well as PAR and Player Efficiency Rating appear to have less of a linear distribution. This can be 
attributed to the scaling methods of each statistic. Since Win Shares and Value Over Replacement Player 
follow a similar scale, with a minimum slightly below 0, and a maximum somewhere in the range of 10, the 
scales match, and each player's value of each metric fits similarly enough to form a linear distribution. 
However, Box Plus Minus ranges from -40 to above 20, so we see the graph centered around 0, where the 
majority of players fall, and going almost straight upwards based on their PAR value. Player Efficiency 
Rating has a similar scale, so a similar effect is shown. In order to see how Points Above Replacement fits 
in terms of all of these accepted metrics, a multiple regression will be run, with the 4 accepted metrics as 
regressors, and with PAR as the independent variable.
\begin{figure}[H]
  \centering
  \includegraphics[scale = 0.6]{MultipleRegression}
  \caption{Multiple Regression with Regressors PER, WS, BPM, and VORP and Independent Variable PAR}
  \label{fig:Fig5}
\end{figure}

The key statistic here is the adjusted R-squared value of 0.6974. This shows that 69.74 percent of variation 
in PAR can be explained by these other 4 accepted metrics. This shows a clear correlation between PAR 
and the metrics, but also shows that PAR has something unique to offer.

@@

\begin{table}[H]
  \caption{PAR Legend}
  \label{tab:PARLegend}
\centering
\begin{tabular}[t]{lccllll}
  \toprule
  Role &  PAR\\
  \midrule
Benchwarmer & Less than -0.43\\
  \midrule
Role Player & -0.43 to 0.08\\
  \midrule
Starter & 0.08 to 1.09\\
  \midrule
All-Star & 1.09 to 1.94\\
 \midrule
Superstar & Greater than 1.94\\
  \bottomrule
\end{tabular}
\end{table}

This legend was calculated based on a quantile calculation of all PAR data. It is not an even distribution, as 
it is assumed that there are many more benchwarmers in the NBA than there are superstars. Thus, 
benchwarmers are defined as the bottom 50 percent of the league, as an NBA roster of about 15 players 
will only give 7 or 8 players significant minutes. Players between the 50th and 75th percentile are defined 
as role players, as they get significant minutes, but do not make an impact enough to be considered a solid 
starter. This is where  a "league average" player is expected to fall, as 0 is contained in this part of the 
legend, and 0 represents a league average player via this metric. Next, the 75th to 90th percentile are 
defined as starters, because only 5 players can start a game, and, more often than not, a team only has 3 
or 4 players who are guaranteed starters. 90th to 95th percentiles represent all-stars, as that is clearly a 
very prestigious area to be a part of. Lastly, it is assumed that only the top 5 percent of players in the 
league can be deemed "superstars", so they comprise the 95th to 100th percentile of the NBA. By this 
method, it is felt that a more realistic legend for PAR has been created as opposed to just breaking up the 
data evenly into 5 groups.
